### 2024-02-05 manuscript.tex
* manuscript.tex: Fix typo.
Update bibliography
* manuscript.tex:
* reference.bib:
Reexport BibLaTeX file.

Recently, studies of the so-called subregular classes, that is,
classes even weaker than regular relations, have proved to be a more
probable upper bound.  Such classes are conceptualized as a hierarchy,
not unlike the traditional Chomsky hierarchy in formal language
theory.  The remaining problem is how many phonological phenomena are
explainable and, more importantly, \textemph{not} explainable by each
class.  In this inquiry, tonal systems post an interesting challenge,
and thus require a more in-depth investigation.

@@

If we entirely discard the idea of explicitly encoding boundaries in
input sequences, we need to derive the same processes as before,
thereby implicitly encoding boundaries in some sense.  What boundary
terms achieve is essentially applying a single transformation to
multiple linear sequences and combining the outputs through some
associative operation, say concatenation.  In other words, the
transformation is \enquote{lifted} to operate on multiple linear
sequences.  By doing so, we modularize the transformation into a
simpler transformation and a universal lift operation.\footnote{This
  operation is precisely a functor, or loosely speaking function of
  type
  \((\alpha \to \beta) \to \mathbb{F}\alpha \to \mathbb{F}\beta\),
  commonly known as \(\mathit{map}\).  \(\mathbb{F}\) should produce a
  type whose values can be \enquote{folded} in the sense of
  \textcite{h99tuem} under a monoid.}

@@

\section{Future Prospect}
\paragraph{Type Theory}
Following \posscite{h69fnc} \enquote{formulae-as-types} conception,
logical formulae correspond to types, and by extension logical calculi
correspond to type systems.  For example, logical conjunction
\(p \land q\) corresponds to product types \(\alpha \times \beta\),
logical disjunction \(p \lor q\) corresponds to sum types
\(\alpha + \beta\), and logical implication \(p \implies q\)
corresponds to function types \(\alpha \to \beta\).  Given the heavy
use of logical formulae in this thesis, one naturally wonders whether
it can benefit from a type-theoretic characterization of transducers.

>>>>

Recently, studies of the so-called subregular classes, that is,
classes even weaker than regular relations, have proved to be a more
probable upper bound.  Such classes are conceptualized as a hierarchy,
not unlike the traditional Chomsky hierarchy in formal language
theory.  The remaining problem is how many phonological phenomena are
explainable and, more importantly, \textemph{not} explainable by each
class.  In this inquiry, tonal systems pose an interesting challenge,
and thus require a more in-depth investigation.

@@

If we entirely discard the idea of explicitly encoding boundaries in
input sequences, we need to derive the same processes as before,
thereby implicitly encoding boundaries in some sense.  What boundary
terms achieve is essentially applying a single transformation to
multiple linear sequences and combining the outputs through some
associative operation, say concatenation.  In other words, the
transformation is \enquote{lifted} to operate on multiple linear
sequences.  By doing so, we modularize the transformation into a
simpler transformation and a universal lift operation.\footnote{This
  operation is precisely a functor, or loosely speaking function of
  type
  \((\alpha \to \beta) \to \mathbb{F}\alpha \to \mathbb{F}\beta\),
  commonly known as \(\mathit{map}\).  \(\mathbb{F}\) should produce a
  type whose values can be \enquote{folded} in the sense of
  \textcite{h99tuemf} under a monoid.}

@@

\section{Future Prospect}
\paragraph{Type Theory}
Following \posscite{h80fnc} \enquote{formulae-as-types} conception,
logical formulae correspond to types, and by extension logical calculi
correspond to type systems.  For example, logical conjunction
\(p \land q\) corresponds to product types \(\alpha \times \beta\),
logical disjunction \(p \lor q\) corresponds to sum types
\(\alpha + \beta\), and logical implication \(p \implies q\)
corresponds to function types \(\alpha \to \beta\).  Given the heavy
use of logical formulae in this thesis, one naturally wonders whether
it can benefit from a type-theoretic characterization of transducers.
